The Kapowski Chronicles: A Complete, Volumetric Cortical Thickness Open Source Pipeline with Evaluation on Public Data

### 2013-06-04 KapowskiChronicles/methods.tex
ENH:  Added captions.

Cortical label propagation to each individual subject for all data sets
described below is performed using the PICSL multi-atlas joint label fusion
algorithm described in \cite{wang2013} which recently topped the competition
at the MICCAI 2012 Grand Challenge on Multi-Atlas Labeling and is also 
distributed with the ANTs toolkit.  .

@@

In total, we processed 1202 T1-weighted images from four different
public data sets to obtain the corresponding cortical thickness maps.                           
The four data sets are described below:

\paragraph{IXI}
The IXI data%
\footnote{
http://biomedic.doc.ic.ac.uk/brain-development/
}
 used for the evaluation consists of 577 healthy subjects imaged at three sites 
using several modalities (T1-weighted, T2-weighted, proton density, magnetic 
resonance angiography, and diffusion tensor imaging).  The 
database also consists of  demographic information such as age, weight,
height, ethnicity, occupation category, educational level, and marital status.
The number of subjects spanning a range of demographic characteristics makes
this a rich data set for validating and exploring correlations with cortical 
thickness measured using the ANTs pipeline.

\paragraph{Oasis}
The Open Access Series of Imaging Studies (OASIS)%
\footnote{
http://www.oasis-brains.org/
}
 project consists of 416
(160 males and 256 females) T1-weighted images spanning 
the ages between 18 and 96 with 100 of these subjects having been 
diagnosed with very mild to moderate Alzheimer's disease.  
All subjects are right-handed.  Additional processing is included
with the distribution including bias corrected and segmented images
(gray, white and CSF matters).

\paragraph{NKI}
In support of open science, the 1,000 Functional Connectomes Project%
\footnote{ 
http://fcon\_1000.projects.nitrc.org
}
was initiated on December 11, 2009 by various members of the MRI community
seeking to form collaborative partnerships with imaging institutions for 
sharing well-documented multimodal image sets accompanied by phenotypic data.
This has resulted in the The Nathan Klein Institute (NKI)/Rockland sample
consisting of (at the time of download, September 22, 2012), 186 T1-weighted
images (87 females and 99 males).

\paragraph{Kirby}
The Multi-Modal MRI Reproducibility Resource%
\footnote{
http://www.nitrc.org/projects/multimodal/
}, 
or more informally the Kirby
data set, was originally described in \cite{landman2011} consisting of 
21 subjects (10 female and 11 male) and featuring a rich multiple modality and 
repeated acquisition schedule.

>>>>

Cortical label propagation to each individual subject for all data sets
described below was performed using the PICSL multi-atlas joint label fusion
algorithm described in \cite{wang2013} which recently topped the competition
at the MICCAI 2012 Grand Challenge on Multi-Atlas Labeling and is also 
distributed with the ANTs toolkit.  Cortical thickness values are averaged
within each label using only the non-zero voxels from the cortical thickness map.

@@

In total, we processed 1205 T1-weighted images from four different
public data sets to obtain the corresponding cortical thickness maps.                           
The four data sets are:

\paragraph{IXI}
The IXI data%
\footnote{
http://biomedic.doc.ic.ac.uk/brain-development/
}
consists of 561 healthy subjects (312 females, 249 males) imaged at three sites 
with several modalities acquired (T1-weighted, T2-weighted, proton density, magnetic 
resonance angiography, and diffusion tensor imaging).  The 
database also consists of  demographic information such as date of birth, date
of scan, weight,
height, ethnicity, occupation category, educational level, and marital status.
Several subjects were removed during the analysis since certain
demographic information was missing preventing an accurate estimate of 
the age at the time of image acquisition.

\paragraph{Oasis}
The Open Access Series of Imaging Studies (OASIS)%
\footnote{
http://www.oasis-brains.org/
}
 project consists of 416
(160 males, 256 females) T1-weighted images spanning 
the ages between 18 and 96 with 100 of these subjects having been 
diagnosed with very mild to moderate Alzheimer's disease.  
All subjects are right-handed.  Additional processing is included
with the distribution including bias corrected and segmented images
(gray, white and CSF matters).

\paragraph{NKI}
In support of open science, the 1,000 Functional Connectomes Project%
\footnote{ 
http://fcon\_1000.projects.nitrc.org
}
was initiated on December 11, 2009 by various members of the MRI community
seeking to form collaborative partnerships with imaging institutions for 
sharing well-documented multimodal image sets accompanied by phenotypic data.
This resulted in the Nathan Klein Institute (NKI)/Rockland sample
consisting of (at the time of download, September 22, 2012), 186 T1-weighted
images (87 females, 99 males).

\paragraph{Kirby}
The Multi-Modal MRI Reproducibility Resource%
\footnote{
http://www.nitrc.org/projects/multimodal/
}, 
or more informally the Kirby
data set, was originally described in \cite{landman2011} consisting of 
21 subjects (10 females, 11 males) and featuring a rich multiple modality and 
repeated acquisition schedule.
